The SMT Competition 2015--2018

### 2019-08-21 2018/report/Reviews_67398_Revised_Response.txt

> * Quality
>
> - The paper still contains a number of issues, minor or not, detailed at the end of this review.
>
> -  In Section 2 the fact that "appointment should happen ... " is of relative interest and could be omitted. The same holds for the day in which the events took place.

TODO

> * Rules
>
> - basically incorrect results are "ignored" by omitting the benchmark if the status is not known - this comment still remains. The authors updated the text. I see their points and analysis, which I appreciated, through I think that this is an issue that should be dealt with more care. Correctness is very important for solvers when checking in particular real benchmarks (HW- and SW-verification, etc).

DONE (updated to better motivate the removal of benchmarks with
disagreements; of course we agree that correctness is important)

@@

>  - "and in 2018, there were" ->   "while in 2018, there were"

DONE

> - e \in \{0,1 \} is defined, but than it is said to be the number of returned statuses...are they aligned? Please clarify

DONE (changed to clarify that e \in \{0,1\} only for the Main Track)

@@

>  - "and not Vampire." -> - "and not by Vampire."

DONE

>  Section 9
>
> - "The last FLoC Olympiad was a period of ..." -> are you referring to "the time between the two FLoC Olympiads" ?

WONTFIX (we are referring to the time between the two FLoC Olympic
Games; this is correct usage of the word Olympiad)

### 2019-08-21 2018/report/SMT-COMP.tex
Motivate removal of disagreements

\paragraph{Benchmarks with Unknown Status.}
Another paradigm shift concerns the treatment of benchmarks with
unknown status.  Because of the difficulty to judge solver responses
for such benchmarks, SMT Competitions until 2015 only used benchmarks
whose status was known (i.e., that had been solved previously by
existing SMT solvers).  In 2015, 30,717 non-incremental benchmarks
from the SMT Library were not used for the competition because their
status was unknown.  However, this approach was criticized for
imitating existing solvers rather than truly innovating.  In~2016,
the SMT Library contained 29,724 non-incremental benchmarks with
unknown status; solver performance on these was evaluated but reported
separately.  Since 2017, all non-incremental benchmarks are eligible
for the competition's \maintrack regardless of status, and they
directly affect the competition results.  Solver responses for such
benchmarks are assumed to be correct, unless there is a disagreement
between two or more (otherwise sound e.g. on problems with known status) solvers.  Benchmarks with
disagreements are removed from the competition results.  This conservative approach was chosen over a voting system as this situation is expected to be rare as the SMT-LIB organisers go to a significant effort prior to each competition to update the statuses of problems. A manual investigation is therefore preferred over an automated resolution. Disagreements are reported to the solvers involved and in all cases have led to bugs in solvers being identified and fixed.
In 2016,
there were disagreements on 79 benchmarks; in 2017, only one benchmark
was removed; while in 2018, there were no disagreements between
otherwise sound solvers.

>>>>

\paragraph{Benchmarks with Unknown Status.}
Another paradigm shift concerns the treatment of benchmarks with
unknown status.  Because of the difficulty to judge solver responses
for such benchmarks, SMT Competitions until 2015 only used benchmarks
whose status was known (i.e., that had been solved previously by
existing SMT solvers).  In 2015, \num{30717} non-incremental benchmarks
from the SMT Library were not used for the competition because their
status was unknown.  However, this approach was criticized for
imitating existing solvers rather than truly innovating.  In~2016,
the SMT Library contained \num{29724} non-incremental benchmarks with
unknown status; solver performance on these was evaluated but reported
separately.  Since 2017, all non-incremental benchmarks are eligible
for the competition's \maintrack regardless of status, and they
directly affect the competition results.  Solver responses for such
benchmarks are assumed to be correct, unless there is a disagreement
between two or more solvers that are otherwise (i.e., on problems with
known status) sound.  Benchmarks with disagreements are removed from
the competition results.  This conservative approach was chosen over a
voting system as the latter is unreliable (especially in divisions
with few solvers), could lead to a solver being punished wrongly, and
could be gamed by entering multiple copies of a solver into the
competition.  Moreover, the size and time frame of the competition
demand an automated resolution.  Disagreements are reported to the
solver developers involved, who typically perform a manual
investigation at their leisure, and in all cases have led to bugs in
solvers being identified and fixed.  In 2016, there were disagreements
on 79 benchmarks; in 2017, only one benchmark was removed; while in
2018, there were no disagreements between otherwise sound solvers.
